Nonlinear Tidal Dissipation in Binary White Dwarfs

### 2019-03-03 proposal/FINESST/Su_FINESST_2019.tex
update w/ MESA use ref

As MESA is a 1D stellar evolution code, I will easily have sufficient
computational resources to carry out this investigation.

>>>>

This objective is very feasible using the resources available to me at Cornell.
Many members of my research group have used MESA in their work on tides in WDs
(e.g.\ \cite{fullerII,fullerIV,vick}) and will be able to advise me.
Additionally, as MESA is a 1D stellar evolution code, I will have sufficient
computing resources to carry out this investigation.
